Official Development Assistance and Institutional Quality on Undeveloped countries

### 2024-09-13 ODA/ODA.Rmd
variables exc y modelos finales

dem_avg <- read_csv("Data/Electoral Democracy Index.csv")

@@

exc_avg <- read_csv("Data/Exclusion by Gender.csv")

datos_paper <- datos_paper %>% merge(exc_avg %>% select(1, 2), by.x = 'year', by.y = 'Year', all.x = TRUE) %>%
                mutate(exc_high = case_when(is.na(exc) ~ NA_real_, 
                                            is.na(`*World`) ~ NA_real_,
                                            exc >= `*World` ~ 1, 
                                            TRUE ~ 0)) %>% select(-`*World`)

lib_avg <- read_csv("DATA/political-civil-liberties-index.csv") %>% filter(Code == 'OWID_WRL')

@@

## Modelos  {.tabset .tabset-fade}
```{r}
# 1993 - 2022
datos_model <- country_class %>% filter(income != 'High income') %>% merge(datos_paper) %>%
  select(iso2c, year, region, income, ODA.GNI, ODA.ALL, ODA.PC, GDP.PC, GDP.PPP, 
         GROW, hdi, LIB, lib_high, dem, dem_high, exc, exc_high) %>%
  arrange(iso2c, year) %>% filter(year >= first_y, year <= last_y, !iso2c %in% filtro_c)
```

@@

```{r}
formulas <- list(
  # list(name = 'modelo1', vd = 'hdi', vi = c('ODA.GNI','GDP.PPP','GROW','LIB','dem','exc'), vint = c()),
  # list(name = 'modelo2', vd = 'hdi', vi = c('ODA.GNI','GDP.PC' ,'GROW','LIB','dem','exc'), vint = c()),
  # list(name = 'modelo3', vd = 'hdi', vi = c('ODA.GNI','GDP.PC' ,'GROW','LIB','dem'),       vint = c()),
  # list(name = 'modelo4', vd = 'hdi', vi = c('GDP.PC' ,'GROW', 'dem', 'LIB'), vint = c('ODA.GNI*dem_high')),
  # list(name = 'modelo5', vd = 'hdi', vi = c('GDP.PC' ,'GROW', 'dem'), vint = c('ODA.GNI*dem_high')),
  # list(name = 'modelo6', vd = 'hdi', vi = c('GDP.PC' ,'GROW', 'exc'), vint = c('ODA.GNI*exc_high')),
  # list(name = 'Original', vd = 'hdi', vi = c('GDP.PC' ,'GOV'), vint = c('ODA.PC*GOV_high')),
  # list(name = 'modelo7', vd = 'hdi', vi = c('GDP.PC' ,'GROW', 'dem'), vint = c('ODA.PC*dem_high')),
  # list(name = 'modelo8', vd = 'hdi', vi = c('GDP.PC' ,'GROW', 'exc'), vint = c('ODA.PC*exc_high')),
  # list(name = 'modelo9', vd = 'hdi', vi = c('GDP.PC' ,'GROW', 'LIB'), vint = c('ODA.PC*lib_high')),
  # list(name = 'modelo10', vd = 'GDP.PC', vi = c('ODA.PC', 'hdi' ,'GROW', 'LIB', 'dem', 'exc'), vint = c()),
  # list(name = 'modelo11', vd = 'GDP.PC', vi = c('ODA.PC', 'hdi' ,'GROW', 'dem', 'exc'), vint = c()),
  # list(name = 'modelo12', vd = 'GDP.PC', vi = c('hdi' ,'GROW', 'dem'), vint = c('ODA.PC*dem_high')),
  # list(name = 'modelo13', vd = 'GDP.PC', vi = c('hdi' ,'GROW', 'exc'), vint = c('ODA.PC*exc_high')),
  # list(name = 'gdp modelo14', vd = 'GDP.PC', vi = c('ODA.PC' ,'hdi','GROW', 'dem'), vint = c(), vf = c('factor(region)', 'factor(income)')),
  # list(name = 'gdp modelo15', vd = 'GDP.PC', vi = c('ODA.PC' ,'hdi','GROW', 'exc'), vint = c(), vf = c('factor(region)', 'factor(income)')),
  #list(name = 'gdp modelo16', vd = 'GDP.PC', vi = c('ODA.PC' ,'GROW', 'dem'), vint = c(), vf = c('factor(region)', 'factor(income)')),
  list(name = 'gdp modelo17', vd = 'GDP.PC', vi = c('ODA.PC' ,'GROW', 'exc'), vint = c(), vf = c('factor(region)', 'factor(income)')),
  # list(name = 'gdp modelo18', vd = 'GDP.PC', vi = c('ODA.PC' ,'GROW', 'LIB'), vint = c(), vf = c('factor(region)', 'factor(income)')),
  #list(name = 'hdi modelo14', vd = 'hdi', vi = c('ODA.PC', 'GDP.PC', 'dem'), vint = c(), vf = c('factor(region)', 'factor(income)')),
  #list(name = 'hdi modelo15', vd = 'hdi', vi = c('ODA.PC', 'GDP.PC', 'exc'), vint = c(), vf = c()),
  # list(name = 'hdi modelo19', vd = 'hdi', vi = c('ODA.PC', 'GDP.PC', 'LIB'), vint = c(), vf = c()),
  list(name = 'hdi modelo20', vd = 'hdi', vi = c('GDP.PC', 'exc'), vint = c('ODA.PC*exc_high'), vf = c()),
  #list(name = 'hdi modelo21', vd = 'hdi', vi = c('GDP.PC', 'dem'), vint = c('ODA.PC*dem_high'), vf = c()),
  #list(name = 'hdi modelo22', vd = 'hdi', vi = c('GDP.PC', 'exc'), vint = c('ODA.PC*exc_high'), vf = c('factor(region)', 'factor(income)'))
  list(name = 'hdi modelo20', vd = 'GDP.PC', vi = c('GROW', 'exc'), vint = c('ODA.PC*exc_high'), vf = c())
  )
```

>>>>

dem_avg <- read_csv("Data/Electoral Democracy Index.csv", show_col_types = FALSE)

@@

exc_avg <- read_csv("Data/Exclusion by Gender.csv", show_col_types = FALSE)

datos_paper <- datos_paper %>% merge(exc_avg %>% select(1, 2), by.x = 'year', by.y = 'Year', all.x = TRUE) %>%
                mutate(exc_high = case_when(is.na(exc) ~ NA_real_, 
                                            is.na(`*World`) ~ NA_real_,
                                            exc >= `*World` ~ 1, 
                                            TRUE ~ 0)) %>% select(-`*World`) %>%
                mutate(no_exc = 1 - exc, no_exc_high = 1 - exc_high, inv_exc = 1 / exc, inv_exc_high = 1 - exc_high)

lib_avg <- read_csv("DATA/political-civil-liberties-index.csv", show_col_types = FALSE) %>% filter(Code == 'OWID_WRL')

@@

## Modelos  {.tabset .tabset-fade}
```{r}
# 1993 - 2022
datos_model <- country_class %>% filter(income != 'High income') %>% merge(datos_paper) %>%
  select(iso2c, year, region, income, ODA.GNI, ODA.ALL, ODA.PC, GDP.PC, GDP.PPP, 
         GROW, hdi, LIB, lib_high, dem, dem_high, exc, exc_high, no_exc, no_exc_high, inv_exc, inv_exc_high) %>%
  arrange(iso2c, year) %>% filter(year >= first_y, year <= last_y, !iso2c %in% filtro_c)
```

@@

```{r}
formulas <- list(
  # list(name = 'modelo1', vd = 'hdi', vi = c('ODA.GNI','GDP.PPP','GROW','LIB','dem','exc'), vint = c()),
  # list(name = 'modelo2', vd = 'hdi', vi = c('ODA.GNI','GDP.PC' ,'GROW','LIB','dem','exc'), vint = c()),
  # list(name = 'modelo3', vd = 'hdi', vi = c('ODA.GNI','GDP.PC' ,'GROW','LIB','dem'),       vint = c()),
  # list(name = 'modelo4', vd = 'hdi', vi = c('GDP.PC' ,'GROW', 'dem', 'LIB'), vint = c('ODA.GNI*dem_high')),
  # list(name = 'modelo5', vd = 'hdi', vi = c('GDP.PC' ,'GROW', 'dem'), vint = c('ODA.GNI*dem_high')),
  # list(name = 'modelo6', vd = 'hdi', vi = c('GDP.PC' ,'GROW', 'exc'), vint = c('ODA.GNI*exc_high')),
  # list(name = 'Original', vd = 'hdi', vi = c('GDP.PC' ,'GOV'), vint = c('ODA.PC*GOV_high')),
  # list(name = 'modelo7', vd = 'hdi', vi = c('GDP.PC' ,'GROW', 'dem'), vint = c('ODA.PC*dem_high')),
  # list(name = 'modelo8', vd = 'hdi', vi = c('GDP.PC' ,'GROW', 'exc'), vint = c('ODA.PC*exc_high')),
  # list(name = 'modelo9', vd = 'hdi', vi = c('GDP.PC' ,'GROW', 'LIB'), vint = c('ODA.PC*lib_high')),
  # list(name = 'modelo10', vd = 'GDP.PC', vi = c('ODA.PC', 'hdi' ,'GROW', 'LIB', 'dem', 'exc'), vint = c()),
  # list(name = 'modelo11', vd = 'GDP.PC', vi = c('ODA.PC', 'hdi' ,'GROW', 'dem', 'exc'), vint = c()),
  # list(name = 'modelo12', vd = 'GDP.PC', vi = c('hdi' ,'GROW', 'dem'), vint = c('ODA.PC*dem_high')),
  # list(name = 'modelo13', vd = 'GDP.PC', vi = c('hdi' ,'GROW', 'exc'), vint = c('ODA.PC*exc_high')),
  # list(name = 'gdp modelo14', vd = 'GDP.PC', vi = c('ODA.PC' ,'hdi','GROW', 'dem'), vint = c(), 
  #      vf = c('factor(region)', 'factor(income)')),
  # list(name = 'gdp modelo15', vd = 'GDP.PC', vi = c('ODA.PC' ,'hdi','GROW', 'exc'), vint = c(), 
  #      vf = c('factor(region)', 'factor(income)')),
  # list(name = 'gdp modelo16', vd = 'GDP.PC', vi = c('ODA.PC' ,'GROW', 'dem'), vint = c(), 
  # vf = c('factor(region)', 'factor(income)')),
  # list(name = 'gdp modelo17', vd = 'GDP.PC', vi = c('ODA.PC' ,'GROW', 'exc'), vint = c(), 
  #      vf = c('factor(region)', 'factor(income)')),
  # list(name = 'gdp modelo17 no', vd = 'GDP.PC', vi = c('ODA.PC' ,'GROW', 'no_exc'), vint = c(), 
  #      vf = c('factor(region)', 'factor(income)')),
  list(name = 'gdp modelo17 inv', vd = 'GDP.PC', vi = c('ODA.PC' ,'GROW', 'inv_exc'), vint = c(), 
       vf = c('factor(region)', 'factor(income)')),
  # list(name = 'gdp modelo18', vd = 'GDP.PC', vi = c('ODA.PC' ,'GROW', 'LIB'), vint = c(), vf = c('factor(region)', 'factor(income)')),
  #list(name = 'hdi modelo14', vd = 'hdi', vi = c('ODA.PC', 'GDP.PC', 'dem'), vint = c(), vf = c('factor(region)', 'factor(income)')),
  #list(name = 'hdi modelo15', vd = 'hdi', vi = c('ODA.PC', 'GDP.PC', 'exc'), vint = c(), vf = c()),
  # list(name = 'hdi modelo19', vd = 'hdi', vi = c('ODA.PC', 'GDP.PC', 'LIB'), vint = c(), vf = c()),
  list(name = 'hdi modelo20', vd = 'hdi', vi = c('GDP.PC', 'exc'), vint = c('ODA.PC*exc_high'), vf = c()),
  #list(name = 'hdi modelo21', vd = 'hdi', vi = c('GDP.PC', 'dem'), vint = c('ODA.PC*dem_high'), vf = c()),
  #list(name = 'hdi modelo22', vd = 'hdi', vi = c('GDP.PC', 'exc'), vint = c('ODA.PC*exc_high'), vf = c('factor(region)', 'factor(income)'))
  list(name = 'gdp modelo23', vd = 'GDP.PC', vi = c('GROW', 'exc'), vint = c('ODA.PC*exc_high'), vf = c()),
  # list(name = 'hdi modelo24 inv', vd = 'hdi', vi = c('GDP.PC', 'inv_exc'), vint = c('ODA.PC*inv_exc_high'), vf = c()),
  # list(name = 'gdp modelo25 inv', vd = 'GDP.PC', vi = c('GROW', 'inv_exc'), vint = c('ODA.PC*inv_exc_high'), vf = c())
  list(name = 'gdp modelo26', vd = 'GDP.PC', vi = c('hdi', 'exc'), vint = c('ODA.PC*exc_high'), vf = c())
  )
```

### 2024-09-13 paper.Rmd
variables exc y modelos finales

>>>>

suppressWarnings(
  plot_ly(temp %>% filter(year %in% c(2002, 2012, 2022)), x = ~year, y = ~GDP.PC, color = ~`Income group`, type = "box") %>%
    layout(title = 'PIB per capita en paises de Ingresos Bajos e Ingresos Medios-bajos', boxmode = "group")
)

suppressWarnings(
  plot_ly(temp %>% filter(year %in% c(2002, 2012, 2022)), x = ~year, y = ~GDP.PC, color = ~Region, type = "box") %>%
    layout(title = 'PIB per capita segun Region', boxmode = "group")
)
```
